Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-18 content/abstract.tex
remove abbreviation

\begin{abstract}
    When two methods are invoked on the same object, the dispatch behaviours of these
    method calls will be correlated. If two correlated method calls are polymorphic 
    (i.e., they dispatch to different method definitions depending on the type of 
    the receiver object), a program's interprocedural control flow graph (ICFG)
    will contain infeasible paths. Existing algorithms for dataflow analysis 
    are unable to ignore such infeasible paths, giving rise to loss of precision.

>>>>

\begin{abstract}
    When two methods are invoked on the same object, the dispatch behaviours of these
    method calls will be correlated. If two correlated method calls are polymorphic 
    (i.e., they dispatch to different method definitions depending on the type of 
    the receiver object), a program's interprocedural control flow graph
    will contain infeasible paths. Existing algorithms for dataflow analysis 
    are unable to ignore such infeasible paths, giving rise to loss of precision.
